My titleXXXXXXXXXXXXXXXX

### 2022-03-19 outputs/paper/paper.Rmd
fvdvdv

---
title: "My titleXXXXXXXXXXXXXXXX"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

>>>>

---
title: "My titleXXXXXXXXXXXXXXXX"
subtitle: "My subtitle if needed"
author: 
  - Adam Labas  
  - Krupali Bhavsar
thanks: "Code and data are available at: XXXXXXXXXXXXXXXXXXXXXXX"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---
